---
title: "mamasante introduction"
author: "Joseph Hicks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

mamasante is a tool for applying Dust, Odin, and MCState to fit a semi-stochastic mechanistic disease transmission model to continuously collected prevalence data using particle Markov chain Monte Carlo (pMCMC). Specifically, this package has been developed to fit a semi-stochastic version of 'malariasimulation' to monthly malaria prevalence among pregnant women at first antenatal care (ANC) visit. This vignette walks through a simple example and describes various options and settings that can be applied.

## Understanding 

## Input Data

In this simple example, we will fit our model to simulated monthly prevalence data in children under 5 years old. Data for fitting should be a data frame with at least three columns:

1.  Month (hear formatted as 'yearmon')
2.  The number of inidividuals tested
3.  Of those tested, the number of positive test results

Like so,

```{r, fig.show='hold'}
install.packages(
  "mcstate",
  repos = c("https://mrc-ide.r-universe.dev", "https://cloud.r-project.org"))
install.packages(
  "odin.dust",
  repos = c("https://mrc-ide.r-universe.dev", "https://cloud.r-project.org"))
data_slim <- dplyr::select(mamasante::data_sim,month,positive,tested)
data_slim
```

## Running a pMCMC fitting

The 'run_pmcmc' function is the central tool to fit our model to observed data. It formats the provided dataframe, sets up required functions and parameters, and finally runs the pMCMC. Broadly, the flow of actions is as follows:

1.  Process provided data set, specifically formatting necessary time variables.
2.  Format and declare parameters. These include both constant or known parameter values needed for the malariasimulation and pMCMC parameters that will be fit.
3.  Set particle filter and pMCMC settings.
4.  Run the pMCMC.
5.  Format output.


The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

```         
output: 
  rmarkdown::html_vignette:
    css: mystyles.css
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

```         
output:
  rmarkdown::html_vignette:
    fig_caption: yes
```

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither." ([via](https://twitter.com/hadleywickham/status/504368538874703872))
