---
title: "sifter introduction"
author: "Joseph Hicks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Sifter is a tool for applying Dust, Odin, and MCState to fit a semi-stochastic mechanistic disease transmission model to continuously collected prevalence data using particle Markov chain Monte Carlo (pMCMC). Specifically, this package has been developed to fit a semi-stochastic version of malariasimulation to monthly malaria prevalence among pregnant women at first antenatal care (ANC) visit.

-   Never uses retina figures
-   Has a smaller default figure size
-   Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

```         
output: 
  rmarkdown::html_vignette:
    css: mystyles.css
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

```         
output:
  rmarkdown::html_vignette:
    fig_caption: yes
```

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither." ([via](https://twitter.com/hadleywickham/status/504368538874703872))
